Summary Tables

### 2023-06-21 summary_tables.Rmd

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
ap_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
pa_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
pa_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
scen_names <- rownames(scen_prop)
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

      # Long format and adding new variables
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i,
               scenario = case_when(
                 grepl("scen1", cause) ~ scen_names[1],
                 grepl("scen2", cause) ~ scen_names[2],
                 grepl("scen3", cause) ~ scen_names[3],
                 grepl("scen4", cause) ~ scen_names[4],
                 grepl("scen5", cause) ~ scen_names[5],
               ),
               level1 = case_when(
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when(
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("COPD", cause) ~ "L2: Respiratory",
                 grepl("LRI", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when(
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when(
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        left_join(pop_by_age, by = c("age_cat" = "age")) %>% 
        left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>% 
        mutate(metric_100k = measure / pop_age * 100000,
               metric_100k_sex = measure / pop_age_sex * 100000)

>>>>

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
ap_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
pa_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
pa_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
scen_names <- rownames(io$scen_prop)
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

      # Long format and adding new variables
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i,
               scenario = case_when(
                 grepl("sc_cycle", cause) ~ scen_names[1],
                 grepl("sc_car", cause) ~ scen_names[2],
                 grepl("sc_bus", cause) ~ scen_names[3],
                 grepl("sc_motorcycle", cause) ~ scen_names[4]
               ),
               level1 = case_when(
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when(
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("respiratory", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when(
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("myeloid_leukemia", cause) ~ "L3: Myeloid Leukemia",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when(
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        left_join(pop_by_age, by = c("age_cat" = "age")) %>% 
        left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>% 
        mutate(metric_100k = measure / pop_age * 100000,
               metric_100k_sex = measure / pop_age_sex * 100000)
